1. Create a matrix mat with 5 columns and 10 rows using matrix with random 
values (function rnorm(50)).
```{r}
M1 = matrix(data = rnorm(50), ncol =5, nrow = 10)
M1
```

2. Find the maximum value of each column.
```{r}
rbind(M1, Max = apply(M1, 2, max))

```

3. Find the mean value of each column.
```{r}
rbind(M1, Mean = apply(M1, 2, mean))

```

4. Find minimum value in each row. 
```{r}
cbind(M1, Min = apply(M1, 1, min))
```

5. Sort each column of the table. 
```{r}
apply(M1, 2, function(x) sort(x))
```

6. Find number of values < 0 for each column. Choose your function.
```{r}
rbind(M1, "<0" = apply(M1, 2, function(x) length((x[x<0]))))
```

7. Display s vector with Boolean values TRUE and FALSE. TRUE if there are 
elements> 2 in the column, FALSE if not.
```{r}
s<- sapply(apply(M1,2,function(x) length(x[x>2])), function(x) x>0)
s

```

8. Create a list list1 <- list(observationA = c(1:5, 7:3), observationB = matrix(1:6, nrow=2)). For this list find sum using function lapply.
```{r}
list1 <- list(observationA = c(1:5, 7:3), observationB = matrix(1:6, nrow=2))
list1

lapply(list1, sum)

```

9. For each element of the list1 find maximum and minimum values (range) 
using lapply and sapply.
```{r}
lapply(list1, max)
sapply(list1, max)

lapply(list1, min)
sapply(list1, min)

```

10. For the built-in data set InsectSprays find mean count for each spray
```{r}
names(InsectSprays)
tapply(InsectSprays$count, InsectSprays$spray,mean)
```

